Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-25 R0V0.tex
Minor changes on notation.
Change notation for the derivative of \gamma

A \emph{Riemannian metric on $\mathbb{R}^n$} is a positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$. In a particular coordinate system, for any pair of vectors $\delta_0,\delta_1$ of $\mathbb{R}^n$ the \emph{metric} is defined as the inner product $\langle\delta_0,\delta_{ 1}\rangle_x=\delta_0^\top M(x)\delta_1$, where $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ is a smooth function. Consequently, local notions of norm $|\delta_0|_x^2=\langle\delta_0,\delta_0\rangle_x=:V(x,\delta_0)$ and orthogonality $\langle\delta_0,\delta_1\rangle_x=0$ can be defined. The metric is said to be \emph{bounded} if there exists constant values $\underline{m}>0$ and $\overline{m}>0$ such that, for every $x\in\mathbb{R}^n$, $\underline{m}I_n\leq M(x)\leq \overline{m}I_n$, where $I_n\in\mathbb{R}^{n\times n}$ is the identity matrix. From now, metric stands for a bounded Riemannian metric.

Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $\gamma:[0,1]\to\mathbb{R}^n$ connecting $x_0=\gamma(0)$ to $x_1=\gamma(1)$. The \emph{length} and \emph{energy} of $\gamma$ are, respectively, defined by the values
\begin{align*}
	\ell(\gamma)=&\ \int_0^1\left|\gamma_s(s)\right|_{\gamma(s)}\,ds\\
	e(\gamma)=&\ \int_0^1V\left(\gamma(s),\gamma_s(s)\right)\,ds\;.
\end{align*}
The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them. This curve is said to be a \emph{geodesic} and it is the solution to the optimization problem
\begin{equation}\label{eq:geodesic formulation}
	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{\gamma\in\Gamma(x_0,x_1)}\ell(\gamma)\;.
\end{equation}

@@

	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}. Because $M$ is a block-diagonal matrix, the energy of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
	\begin{equation}\label{eq:geodesic sum}
		e(\varphi)=\int_0^1\sum_{i=1}^N V_i\left(\varphi_i(s_i),\tfrac{\partial \varphi_i}{\partial s_i}(s_i)\right)\,ds\;.
	\end{equation}

@@

	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
	\begin{equation*}
		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(\sigma),k_i^\ast(t,s))\widetilde{\gamma}_i'(\sigma)\,d\sigma\;,
	\end{equation*}
	where $\widetilde{\gamma}_i(\cdot)\in\mathbf{X}(\mathscr{K}(i))$.
	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
\end{proof}

@@

Before showing how the MI \eqref{eq:MI formulation} can be computed in parallel, some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015}.

Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network \eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.

>>>>

A \emph{Riemannian metric on $\mathbb{R}^n$} is a symmetric positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$. In a particular coordinate system, for any pair of vectors $\delta_0,\delta_1$ of $\mathbb{R}^n$ the \emph{metric} is defined as the inner product $\langle\delta_0,\delta_{ 1}\rangle_x=\delta_0^\top M(x)\delta_1$, where $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ is a smooth function. Consequently, local notions of norm $|\delta_0|_x^2=\langle\delta_0,\delta_0\rangle_x=:V(x,\delta_0)$ and orthogonality $\langle\delta_0,\delta_1\rangle_x=0$ can be defined. The metric is said to be \emph{bounded} if there exists constant values $\underline{m}>0$ and $\overline{m}>0$ such that, for every $x\in\mathbb{R}^n$, $\underline{m}I_n\leq M(x)\leq \overline{m}I_n$, where $I_n\in\mathbb{R}^{n\times n}$ is the identity matrix. From now, metric stands for a bounded Riemannian metric.

Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $\gamma:[0,1]\to\mathbb{R}^n$ connecting $x_0=\gamma(0)$ to $x_1=\gamma(1)$. The \emph{length} and \emph{energy} of $\gamma$ are, respectively, defined by the values
\begin{align*}
	\ell(\gamma)=&\ \int_0^1\left|\gamma_s(s)\right|_{\gamma(s)}\,ds\\
	e(\gamma)=&\ \int_0^1V\left(\gamma(s),\gamma_s(s)\right)\,ds\;,
\end{align*}
where the notation $\gamma_s$ stands for the derivative $\tfrac{\partial\gamma}{\partial s}$. The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them. This curve is said to be a \emph{geodesic} and it is the solution to the optimization problem
\begin{equation}\label{eq:geodesic formulation}
	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{\gamma\in\Gamma(x_0,x_1)}\ell(\gamma)\;.
\end{equation}

@@

	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}. Because $M$ is a block-diagonal matrix, the energy of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
	\begin{equation}\label{eq:geodesic sum}
		e(\varphi)=\int_0^1\sum_{i=1}^N V_i\left(\varphi_i(s_i),\frac{\partial \varphi_i}{\partial s_i}(s_i)\right)\,ds\;.
	\end{equation}

@@

	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
	\begin{equation*}
		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(\sigma),k_i^\ast(t,s))\frac{\partial\widetilde{\gamma}_i}{\partial \sigma}(\sigma)\,d\sigma\;,
	\end{equation*}
	where $\widetilde{\gamma}_i(\cdot)\in\mathbf{X}(\mathscr{K}(i))$.
	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
\end{proof}

@@

Before showing how the MI \eqref{eq:MI formulation} can be computed in parallel, some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.

Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. Let $k\in\mathbb{N}_{[1,N]}$ be a constant value and $\{1,\ldots,k\}$ be a path. A \emph{chord} of a path is any edge joining two nonconsecutive nodes.

A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
